---
title: "Linearity analysis of DGVMs"
author: "Beni Stocker and Huanyuan Zhang"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
# output:
#   pdf_document:
#     toc: true
#     toc_depth: 2
---

```{r include=FALSE}
library(dplyr)
library(purrr)
library(tidyr)
library(ggplot2)
library(readr)
library(stringr)
library(here)
library(rgeco) # get it from here: https://github.com/geco-bern/rgeco
library(khroma)
library(cowplot)
```

## Approach

Does (steady-state) SOC storage, simulated in DGVMs, scale with litter inputs? And do litter inputs scale with biomass? To investigate this, we can look at the following relationships:

- The relative enhancement in steady-state SOC vs. the relative enhancement in NPP. $C^\ast$ is the steady-state SOC. It is given by the initial SOC stocks in simulations (spun up to steady state). 
$$
\frac{\Delta C^\ast}{C^\ast} / \frac{\Delta NPP}{NPP_\text{init}}
$$
- The relative enhancement in steady-state SOC vs. the relative enhancement in biomass ($B$).
$$
\frac{\Delta C^\ast}{C^\ast} / \frac{\Delta B}{B_\text{init}}
$$
$\Delta$ is the difference between end and beginning of a transient simulation covering the historical period, where only CO2 changes (hence, soil turnover rates should not change in a typical 1st order kinetics-based SOC model).

Our hypothesis is that these relationships follow the 1:1 line.

$C^\ast$ cannot be extracted directly from simulations. But it can be estimated from the imbalance between soil respiration and litter input before a steady state is reached:
$$
\tau \approx \frac{C(t)}{I(t) -\dot{C}(t)}
$$

Combine this with $\Delta C^\ast=\tau \; \text{NPP}$, to get:
$$
C^\ast = \frac{C(t)}{1 - \frac{\Delta C(t)}{\text{NPP}(t)}}
$$
These variables are extracted from TRENDY S1 simulations as follows:

- $C(t)$: soil C at the end of the simulation (mean over 2008-2017)
- $\Delta C(t)$: Annual change in soil C during the last decade (2008-2017) (`filn_cSoil_change` - MUST BE DIVIDED BY 10!)
- NPP$(t)$: Annual mean NPP during the last decade (2008-2017)

- $\Delta C^\ast$: $C^\ast$ (as defined above) minus soil C during the first decade of the simulation (spun up to steady state)

The same is done with biomass ($B$).


## Process TRENDY v7 files

(Adjust path for `filnams` to select v8 or v7)

From downloaded TRENDY outputs (here, simulation S1: only CO2 is changing), get global fields of: 

1. Multi-annual mean NPP at the beginning of the simulation
2. Multi-annual mean NPP at the end of the simulation
3. Multi-annual mean SOC at the beginning of the simulation
4. Multi-annual mean SOC at the end of the simulation
5. Multi-annual mean biomass at the beginning of the simulation
6. Multi-annual mean biomass at the end of the simulation
7. Change in SOC over a multi-annual period at the end of the simulation (for $\Delta C(t)$)

Simulations should cover 1700-2017 (318 years = time step in NetCDF outputs). But not all do.

- Starting in year 1700: CABLE-POP, CLM5.0, JSBACH, LPX-Bern, LPJ-GUESS, OCN, ORCHIDEE-CNP, SDGVM
- Starting in year 1701: CLASS-CTEM, ISAM, JULES, SURFEX
- Starting in year 1900: DLEM
- Starting in year 1901: ORCHIDEE
- Starting in year 1860: VISIT

Peculiarities of outputs by model prohibiting their processing:

- LPJ: No S1 outputs
- DLEM: failed NPP processing
- LPX-Bern: failed NPP processing
- VISIT: No NPP output available

No separate output for pools (wood, leaf, root)

- CLASS-CTEM
- DLEM
- JSBACH
- JULES
- OCN
- SDGVM (only wood missing, could be derived by `cdo -O sub SDGVM_S1_cVeg.nc SDGVM_S1_cRoot.nc SDGVM_S1_cLeaf.nc`. cWood is then assumed zero: `cdo mulc,0 SDGVM_S1_cLeaf.nc SDGVM_S1_cWood.nc`, and `cdo -O chname,cLeaf,cWood SDGVM_S1_cWood.nc SDGVM_S1_cWood2.nc`, but is not!)
- SURFEX
- VISIT

### Process files: multi-annual mean

Determine for which models we have all the files (cWood and cVeg) to calculate wood mass fractions and create system command.
```{r}
# availvars <- read_csv( "./availvars_trendy_v8_S1.csv" )
# filnams <- read_csv(here("data-raw/filnams_trendy_v8_S1.csv")) %>%
filnams <- read_csv(here("data-raw/filnams_trendy_v7_S1.csv")) %>%
  setNames(c("modl", paste0("filn_", names(.)[-1])))

modls <- filnams |> 
  filter(!is.na(filn_gpp) & !is.na(filn_cVeg) & !is.na(filn_npp) & !is.na(filn_cRoot)) |>

  ## remove models from analysis. See above for reasons for exclusion
  filter(!(modl %in% c("LPJ", "DLEM", "LPX-Bern", "VISIT"))) |>
  
  filter(modl != "SDGVM") |> 
  
  pull(modl)

# datadir <- "~/data/trendy/v8/"  # on beni laptop
# datadir <- "/data_1/trendy/v8"  # on GECO server
datadir <- here::here("data/")

df <- filnams |> 
  
  ## filter based on above
  filter(modl %in% modls) |>
  
  # mutate(dir = paste0("/cluster/home/bestocke/data/trendy/v8/")) |> 
  # mutate(dir = paste0("~/data/trendy/v8/")) |> 
  mutate(dir = datadir) |> 
  mutate_at(vars(starts_with("filn")), ~str_replace(., ".nc", "")) |>
  
  ## get starting year
  left_join(read_csv(here("data-raw/startyear_trendy_v7_S1.csv")), by = "modl") |> 
  rename(
    startyear_init = startyear, 
    startyear_npp_init = startyear_npp,
    startyear_gpp_init = startyear_gpp
    ) |> 
  mutate(
    endyear_init = startyear_init + 9, 
    endyear_npp_init = startyear_npp_init + 9,
    endyear_gpp_init = startyear_gpp_init + 9
    ) |> 
    
  ## create CDO command to convert flux (per seconds) to annual total (per year)
  mutate(
    cmd_npp_units = paste(here("src/get_tot_ann.sh"), filn_npp, dir),
    cmd_gpp_units = paste(here("src/get_tot_ann.sh"), filn_gpp, dir)
    ) |> 
  
  ## create CDO command to take mean across years at simulation start and end
  mutate(
    cmd_cVeg    = paste(here("src/proc_trendy_soc_biomass.sh"), filn_cVeg,    dir, startyear_init,     endyear_init),
    cmd_gpp     = paste(here("src/proc_trendy_soc_biomass.sh"), filn_gpp_ANN, dir, startyear_gpp_init, endyear_gpp_init),
    cmd_npp     = paste(here("src/proc_trendy_soc_biomass.sh"), filn_npp_ANN, dir, startyear_npp_init, endyear_npp_init),
    cmd_cRoot   = paste(here("src/proc_trendy_soc_biomass.sh"), filn_cRoot,   dir, startyear_init,     endyear_init)
    ) |> 
  
  rowwise() |> 
  mutate(
    filn_npp_init     = paste0(filn_npp_ANN, "_INIT_MEAN"),
    filn_npp_final    = paste0(filn_npp_ANN, "_FINAL_MEAN"),

    filn_gpp_init     = paste0(filn_gpp_ANN, "_INIT_MEAN"),
    filn_gpp_final    = paste0(filn_gpp_ANN, "_FINAL_MEAN"),

    filn_cVeg_init    = paste0(filn_cVeg,    "_INIT_MEAN"),
    filn_cVeg_final   = paste0(filn_cVeg,    "_FINAL_MEAN"),
   
    filn_cRoot_init   = paste0(filn_cRoot,   "_INIT_MEAN"),
    filn_cRoot_final  = paste0(filn_cRoot,   "_FINAL_MEAN")
    )
```

Execute function using CDO.
```{r eval=FALSE}
# # xxx test
# df <- df[1,]

## convert NPP and GPP units (worked except for LPX and DLEM)
out <- purrr::map(as.list(df |> pull(cmd_npp_units)), ~system(., intern = TRUE))
# out <- purrr::map(as.list(df |> pull(cmd_gpp_units)), ~system(., intern = TRUE))

## get GPP as a mean over the period at the beginning and the end of the simulations
# out <- purrr::map(as.list(df |> pull(cmd_gpp)),    ~system(., intern = TRUE))

## get NPP as a mean over the period at the beginning and the end of the simulations
out <- purrr::map(as.list(df |> pull(cmd_npp)),    ~system(., intern = TRUE))

## get cVeg as a mean over the period at the beginning and the end of the simulations
out <- purrr::map(as.list(df |> pull(cmd_cVeg)),   ~system(., intern = TRUE))

out <- purrr::map(as.list(df |> pull(cmd_cRoot)),  ~system(., intern = TRUE))
```

## Collect data

... into tidy data frame

```{r}
source(here("R/collect_gdf_bymodl.R"))

gdf <- purrr::map(

  seq(nrow(df)),

  ~collect_gdf_bymodl(

    df$modl[.],
    df$dir[.],

    df$filn_gpp_init[.],
    df$filn_gpp_final[.],

    df$filn_npp_init[.],
    df$filn_npp_final[.],

    df$filn_cVeg_init[.],
    df$filn_cVeg_final[.],

    df$filn_cRoot_init[.],
    df$filn_cRoot_final[.]
        
    )) |> 
  
  bind_rows() |>

  group_by(modl) |>
  nest()
```

## Calculate relationships

```{r}
source(here("R/get_deltas.R"))

gdf <- gdf |>
  mutate(data = purrr::map(data, ~get_deltas(.)))
```

## Plots

### NPP vs GPP

#### Pooled 

```{r}
# sample for even representation, number determined by model with smallest 
# number of gridcells
nsample <- gdf |> 
  mutate(len = purrr::map_int(data, ~nrow(.))) |> 
  pull(len) |> 
  min()

# all models pooled
gg1 <- gdf |>
  mutate(data = purrr::map(data, ~slice_sample(., n = nsample))) |>
  unnest(data) |>
  dplyr::filter(!is.nan(dnpp), !is.nan(dnpp), !is.infinite(dnpp), !is.infinite(dnpp)) |>
  ggplot(aes(x = dgpp, y = dnpp)) +
  geom_hex(bins = 50, show.legend = FALSE) +
  theme_classic() +
  geom_abline(intercept = 0, slope = 1, linetype = "dotted") +
  geom_hline(yintercept = 0, linetype = "dotted") +
  geom_vline(xintercept = 0, linetype = "dotted") +
  khroma::scale_fill_batlowW(trans = "log", reverse = TRUE) +
  xlim(-1, 2) + 
  ylim(-1, 2) +
  labs(
    x = expression(paste(Delta, "GPP/GPP")),
    y = expression(paste(Delta, "NPP/NPP"))
  )

gg2 <- gdf |>
  mutate(data = purrr::map(data, ~slice_sample(., n = nsample))) |>
  unnest(data) |> 
  ggplot(aes(x = l_gpp_npp, y = ..density..)) +
  geom_density(fill = "grey70") +
  theme_classic() +
  geom_hline(yintercept = 0, linetype = "dotted") +
  geom_vline(xintercept = 0, linetype = "dotted") +
  geom_vline(xintercept = 1, linetype = "dotted") +
  xlim(-1, 2.5) + 
  labs(
    x = expression(paste(italic(L)[NPP/GPP]))
  )

cowplot::plot_grid(
  gg1, 
  gg2,
  ncol = 2
)

ggsave(here("fig/gpp_npp_trendy.pdf"), width = 8, height = 4)
```

#### Heat map - by model

```{r}
gdf |>
  unnest(data) |>
  dplyr::filter(!is.nan(dnpp), !is.nan(dcveg), !is.infinite(dnpp), !is.infinite(dcveg)) |>
  ggplot(aes(x = dnpp, y = dcveg)) +
  geom_hex(bins = 50, show.legend = FALSE) +
  theme_classic() +
  geom_abline(intercept = 0, slope = 1, linetype = "dotted") +
  geom_hline(yintercept = 0, linetype = "dotted") +
  geom_vline(xintercept = 0, linetype = "dotted") +
  khroma::scale_fill_batlowW(trans = "log", reverse = TRUE) +
  xlim(-1, 2) + 
  ylim(-1, 2) +
  labs(
    x = expression(paste(Delta, "NPP/NPP")),
    y = expression(paste(Delta, italic(C)[veg], "/", italic(C)[veg]))
  ) +
  facet_wrap(. ~ modl, nrow = 3,  scales = "free") +
  theme(
    legend.position = "none",
    strip.background = element_blank(),
    strip.text = element_text(size = 12, hjust = 0)
    )

ggsave(here("fig/cveg_npp_trendy_bymodel.pdf"), width = 4, height = 4)
```

#### Map - by model

```{r}
tmp <- gdf |>
  unnest(data) |>
  dplyr::filter(!is.nan(dnpp), !is.nan(dcveg), !is.infinite(dnpp), !is.infinite(dcveg))

coast <- rnaturalearth::ne_coastline(
  scale = 110, 
  returnclass = "sf"
  )

map_bymodl <- function(df, modl, coast){
  
  ggplot() +
	  geom_raster(
	    data = df |> 
	      dplyr::filter(modl == modl),
	    aes(x = lon, y = lat, fill = l_npp_cveg),
	    show.legend = TRUE
	    ) +
    geom_sf(
      data = coast,
      colour = 'black',
      linewidth = 0.3
    )  +
    coord_sf(
      ylim = c(-60, 85),
      expand = FALSE
    ) +
    khroma::scale_fill_berlin(
      name = "",
      limits = c(0,2), 
      midpoint = 1, 
      reverse = TRUE
      ) +
    theme_void() +
    labs(
      title = modl
    )
}

map_bymodl(tmp, "CABLE", coast)
```


### Cveg vs NPP

#### Pooled 

```{r}
# sample for even representation, number determined by model with smallest 
# number of gridcells
nsample <- gdf |> 
  mutate(len = purrr::map_int(data, ~nrow(.))) |> 
  pull(len) |> 
  min()

# all models pooled
gg1 <- gdf |>
  mutate(data = purrr::map(data, ~slice_sample(., n = nsample))) |>
  unnest(data) |>
  dplyr::filter(!is.nan(dnpp), !is.nan(dcveg), !is.infinite(dnpp), !is.infinite(dcveg)) |>
  ggplot(aes(x = dnpp, y = dcveg)) +
  geom_hex(bins = 50, show.legend = FALSE) +
  theme_classic() +
  geom_abline(intercept = 0, slope = 1, linetype = "dotted") +
  geom_hline(yintercept = 0, linetype = "dotted") +
  geom_vline(xintercept = 0, linetype = "dotted") +
  khroma::scale_fill_batlowW(trans = "log", reverse = TRUE) +
  xlim(-1, 2) + 
  ylim(-1, 2) +
  labs(
    x = expression(paste(Delta, "NPP/NPP")),
    y = expression(paste(Delta, italic(C)[veg], "/", italic(C)[veg]))
  )

gg2 <- gdf |>
  mutate(data = purrr::map(data, ~slice_sample(., n = nsample))) |>
  unnest(data) |> 
  ggplot(aes(x = l_npp_cveg, y = ..density..)) +
  geom_density(fill = "grey70") +
  theme_classic() +
  geom_hline(yintercept = 0, linetype = "dotted") +
  geom_vline(xintercept = 0, linetype = "dotted") +
  geom_vline(xintercept = 1, linetype = "dotted") +
  xlim(-1, 2.5) + 
  labs(
    x = expression(paste(italic(L)[Cveg/NPP]))
  )

cowplot::plot_grid(
  gg1, 
  gg2,
  ncol = 2
)

ggsave(here("fig/cveg_npp_trendy.pdf"), width = 8, height = 4)
```

#### Heat map - by model

```{r}
gdf |>
  unnest(data) |>
  dplyr::filter(!is.nan(dnpp), !is.nan(dcveg), !is.infinite(dnpp), !is.infinite(dcveg)) |>
  ggplot(aes(x = dnpp, y = dcveg)) +
  geom_hex(bins = 50, show.legend = FALSE) +
  theme_classic() +
  geom_abline(intercept = 0, slope = 1, linetype = "dotted") +
  geom_hline(yintercept = 0, linetype = "dotted") +
  geom_vline(xintercept = 0, linetype = "dotted") +
  khroma::scale_fill_batlowW(trans = "log", reverse = TRUE) +
  xlim(-1, 2) + 
  ylim(-1, 2) +
  labs(
    x = expression(paste(Delta, "NPP/NPP")),
    y = expression(paste(Delta, italic(C)[veg], "/", italic(C)[veg]))
  ) +
  facet_wrap(. ~ modl, nrow = 3,  scales = "free") +
  theme(
    legend.position = "none",
    strip.background = element_blank(),
    strip.text = element_text(size = 12, hjust = 0)
    )

ggsave(here("fig/cveg_npp_trendy_bymodel.pdf"), width = 4, height = 4)
```

#### Map - by model

```{r}
tmp <- gdf |>
  unnest(data) |>
  dplyr::filter(!is.nan(dnpp), !is.nan(dcveg), !is.infinite(dnpp), !is.infinite(dcveg))

coast <- rnaturalearth::ne_coastline(
  scale = 110, 
  returnclass = "sf"
  )

map_bymodl <- function(df, modl, coast){
  
  ggplot() +
	  geom_raster(
	    data = df |> 
	      dplyr::filter(modl == modl),
	    aes(x = lon, y = lat, fill = l_npp_cveg),
	    show.legend = TRUE
	    ) +
    geom_sf(
      data = coast,
      colour = 'black',
      linewidth = 0.3
    )  +
    coord_sf(
      ylim = c(-60, 85),
      expand = FALSE
    ) +
    khroma::scale_fill_berlin(
      name = "",
      limits = c(0,2), 
      midpoint = 1, 
      reverse = TRUE
      ) +
    theme_void() +
    labs(
      title = modl
    )
}

map_bymodl(tmp, "CABLE", coast)
```

### Croot vs Cveg

All models pooled.
```{r}
# sample for even representation, number determined by model with smallest 
# number of gridcells
nsample <- gdf |> 
  mutate(len = purrr::map_int(data, ~nrow(.))) |> 
  pull(len) |> 
  min()

# all models pooled
gg1 <- gdf |>
  mutate(data = purrr::map(data, ~slice_sample(., n = nsample))) |>
  unnest(data) |>
  dplyr::filter(!is.nan(dcroot), !is.nan(dcveg), !is.infinite(dcroot), !is.infinite(dcveg)) |>
  ggplot(aes(x = dcveg, y = dcroot)) +
  geom_hex(bins = 50, show.legend = FALSE) +
  theme_classic() +
  geom_abline(intercept = 0, slope = 1, linetype = "dotted") +
  geom_hline(yintercept = 0, linetype = "dotted") +
  geom_vline(xintercept = 0, linetype = "dotted") +
  khroma::scale_fill_batlowW(trans = "log", reverse = TRUE) +
  xlim(-1, 2) + 
  ylim(-1, 2) +
  labs(
    x = expression(paste(Delta, italic(C)[veg], "/", italic(C)[veg])),
    y = expression(paste(Delta, italic(C)[root], "/", italic(C)[root]))
  )

gg2 <- gdf |>
  mutate(data = purrr::map(data, ~slice_sample(., n = nsample))) |>
  unnest(data) |> 
  ggplot(aes(x = l_croot_cveg, y = ..density..)) +
  geom_density(fill = "grey70") +
  theme_classic() +
  geom_hline(yintercept = 0, linetype = "dotted") +
  geom_vline(xintercept = 0, linetype = "dotted") +
  geom_vline(xintercept = 1, linetype = "dotted") +
  xlim(-1, 2.5) + 
  labs(
    x = expression(paste(italic(L)[Croot/Cveg]))
  )

cowplot::plot_grid(
  gg1, 
  gg2,
  ncol = 2
)

ggsave(here("fig/croot_cveg_trendy.pdf"), width = 8, height = 4)
```

By model: heat plot
```{r}
gdf |>
  unnest(data) |>
  dplyr::filter(!is.nan(dcroot), !is.nan(dcveg), !is.infinite(dcroot), !is.infinite(dcveg)) |>
  ggplot(aes(x = dcveg, y = dcroot)) +
  geom_hex(bins = 50, show.legend = FALSE) +
  theme_classic() +
  geom_abline(intercept = 0, slope = 1, linetype = "dotted") +
  geom_hline(yintercept = 0, linetype = "dotted") +
  geom_vline(xintercept = 0, linetype = "dotted") +
  khroma::scale_fill_batlowW(trans = "log", reverse = TRUE) +
  xlim(-1, 2) + 
  ylim(-1, 2) +
  labs(
    x = expression(paste(Delta, italic(C)[veg], "/", italic(C)[veg])),
    y = expression(paste(Delta, italic(C)[root], "/", italic(C)[root]))
  ) +
  facet_wrap(. ~ modl, nrow = 3,  scales = "free") +
  theme(
    legend.position = "none",
    strip.background = element_blank(),
    strip.text = element_text(size = 12, hjust = 0)
    )

ggsave(here("fig/croot_cveg_trendy_bymodel.pdf"), width = 4, height = 4)
```
